\Large Generative Dynamics of Supreme Court Citations: \\ Analysis with a New Statistical Model

### 2020-08-31 Tex/PA_rr/main.tex
completed first round of revisions

\subsubsection{Covariate Terms}
Effects of the exogenous covariates included in the c-ERGM are presented in Figure \ref{SCC_results_2}. Most of the exogenous covariate effects align with expectations and have relatively stable parameter estimates over time. We find that cases are more likely to cite those that (1) have been decided most recently, (2) were authored by the same justice, (3) are in the same issue area, and (4) have not been overruled. Surprisingly, we do not find consistent effects for majority coalition size or for the two covariates that involve justice ideology. The effect of majority coalition size was generally not statistically significant until the later portion of the period examined; ideological distance between two cases had signs and significance levels that are highly inconsistent; and the ideological breadth of the potentially cited case was effectively zero for the entire period.

These results leave open the question of whether and how citations are shaped by ideological factors. While we did not formally hypothesize about temporal dynamics in the effects, a closer look at the observed trends allows us to identify some patterns that suggest directions for future research in this area. In this discussion, we focus on the shift in the effect of ideological distance beginning with the Rehnquist court and extending into the Roberts court.

>>>>

\subsubsection{Covariate Terms}
Effects of the exogenous covariates included in the c-ERGM are presented in Figure \ref{SCC_results_2}. Most of the exogenous covariate effects align with expectations and have relatively stable parameter estimates over time. We find that cases are more likely to cite those that (1) have been decided most recently, (2) were authored by the same justice, (3) are in the same issue area, and (4) have not been overruled. Surprisingly, we do not find consistent effects for majority coalition size or for the two covariates that involve justice ideology. The effect of majority coalition size was generally not statistically significant until the later portion of the period examined; ideological distance between two cases had signs and significance levels that are highly inconsistent; and the effect of the ideological breadth of the potentially cited case was effectively zero for the entire period. A purely measurement-based explanation of our findings is that we need a more precise measure of the ideological position of an opinion, as far as citation behavior goes, than the median ideal point of the justice in the majority coalition. Clustering that results from ideological homophily that is not effectively accounted for by our measure would be picked up, in part, by our measures of transitivity, which are statistically and substantively significant throughout the period studied. However, we do observe connections between our findings and the literature on decision-making on the Supreme Court.

Our results leave open the question of whether and how citations are shaped by ideological factors. While we did not formally hypothesize about temporal dynamics in the effects, a closer look at the observed trends allows us to identify some patterns that suggest directions for future research in this area. In this discussion, we focus on the shift in the effect of ideological distance beginning with the Rehnquist court and extending into the Roberts court.

### 2020-08-31 Tex/PA_rrmemo/PA_RnR_memo.tex
completed first round of revisions

\noindent \textbf{Addressed:}  BRUCE, TO DO.\\

@@

\noindent \textbf{Addressed:}  We agree that the original write-up of the dependence effects fell short in terms of both explaining how to interpret the effects, and providing guidance regarding how we made a number of specification choices. For each dependence effect we revised the coverage in three directions. First, we revised and expanded our explanations of both the intuitive and substantive interpretations of the effect. Second, we provided justifications for functional form and hyperparameter specifications (e.g., the decay parameters in gwidegree and gwesp). Third, we removed technical jargon and mathematical expressions that were not necessary for explaining and justifying what we did.

@@

\noindent \textbf{Addressed:} We now mention in the paper that we us \textbf{R} for the implementation of our model and that the code is based on the \textbf{ergm}-package. Furthermore, we note that we have developed a wrapper R-package of \textbf{ergm}, called \textbf{cERGM}, to conveniently fit citation networks using c-ERGMs.  \\

@@

\noindent \textbf{Addressed:}  \\

>>>>

\noindent \textbf{Addressed:}  Please see our response to R2.3. .\\

@@

\noindent \textbf{Addressed:}  We agree that the original write-up of the dependence effects fell short in terms of both explaining how to interpret the effects, and providing guidance regarding how we made a number of specification choices. For each dependence effect we revised the coverage in three directions. First, we revised and expanded our explanations of both the intuitive and substantive interpretations of the effect. Second, we provided justifications for functional form and hyperparameter specifications (e.g., the decay parameters in gwidegree and gwesp). Third, we removed technical jargon and mathematical expressions that were not necessary for explaining and justifying what we did.   \\

@@

\noindent \textbf{Addressed:} We now mention in the paper that we use R for the implementation of our model and that the code is based on extensions of the ergm-package. Furthermore, we note that we have developed a wrapper R-package of ergm, called cERGM, to conveniently fit citation networks using c-ERGMs.  \\

@@

\noindent \textbf{Addressed:}  This comment raises an important point that we now discuss in the results section. If the median justice in the majority coalition is not a precise measure of the ideological position of an opinion, some of the clustering that may result from ideological homophily in citations would be picked up in the transitivity terms. Unfortunately, there is no way (at least that we can think of) to test for this without improving upon the measure of opinion ideology.
